---
title: "Statistical Inference Course Project 1"
author: "Gerardo Figueroa"
date: "October 19, 2020"
output: 
  pdf_document
---
## Statistical Inference Final Project Part 2

This report pretends to analyze the data from ToothGrowth dataset.

1. Load the ToothGrowth data and perfom basic analysis. 
2. Provide a basic summary of the data.
3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. 
4. Report conclusions and the reasons to back them up.

Start program.  Load ToothGrowth Data and investigate its structure
```{r message=FALSE}
library(datasets)
library(dplyr)
library(ggplot2)
# Load ToothGrowth Data
data("ToothGrowth")
str(ToothGrowth)
```

len : Tooth Length is numeric  
supp: Supplement is Factor consisting of OJ and VC  
dose: Dosage is numeric.  As it is just 0.5, 1 and 2, we will have to convert it to factor so that it is easier for analysis  

Doing a quick plot to check for any potential paterns
```{r echo=FALSE, message=FALSE}
qplot(supp,len, data = ToothGrowth, colour = dose)
```

There is are several apparent relations between supp and dose.  Let's boxplot to explore further.

```{r echo=FALSE, message=FALSE}
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
# Boxplot for better view
g <- ggplot(ToothGrowth, aes(x=dose, y=len, colour=supp)) + 
  geom_boxplot()
g
```

We noticed:
1. There is a trend between dose and len.  
2. There is a trend between dose and supp.

## Hypothesis Testing No.1: Overall impact of dosage on tooth growth
###Null Hypothesis - There is no effect of dosage on tooth growth
###Alternate Hypothesis - Higer doses produce greater tooth growth. 

```{r}
# arrange our dateset
dose05 <- filter(ToothGrowth, dose == 0.5)
dose1 <- filter(ToothGrowth, dose == 1)
dose2 <- filter(ToothGrowth, dose == 2)
```
**Comparing dosage of 1mg vs 0.5mg**
```{r}
# compare between dose of 0.5 and 1
t.test(dose1$len, dose05$len, alternative = "greater")
```
As P value is less than 0.001, it is highly significant and we can reject the null hypothesis

**Comparing dosage of 2mg vs 1mg**
```{r}
t.test(dose2$len, dose1$len, alternative = "greater")
```
As P value is less than 0.001, it is highly significant and we reject the null hypothesis

So in both casess, the null hypothesis is rejected.  
**We accept the althernative: higher dosages do have a positive influence on toothgrowth. **

##Hypothesis Testing No 2: Differences between supplements by dosage
###Null Hypothesis - There is no effect between supplement OJ and VC
###Alternate Hypothesis - OJ is better on toothgrowth than VC
Three tests will be done and compared based on dosages.

**Dosage: 0.5mg**
```{r}
OJdose05 <- filter(dose05, supp == "OJ")
VCdose05 <- filter(dose05, supp == "VC")
t.test(OJdose05$len, VCdose05$len, alternative = "greater")
```
P value is lower than 0.05. The null hypothesis is rejected.  
The alternative is accepted: OJ is a better supplement than VC at dosage of 0.5mg

**Dosage: 1mg**
```{r}
OJdose1 <- filter(dose1, supp == "OJ")
VCdose1 <- filter(dose1, supp == "VC")
t.test(OJdose1$len, VCdose1$len, alternative = "greater")
```
P value is lower than 0.05.  The null hypothesis is rejected.  
We accept the alternative: OJ is a better supplement than VC at dosage of 1mg

**Dosage: 2mg**
```{r}
OJdose2 <- filter(dose2, supp == "OJ")
VCdose2 <- filter(dose2, supp == "VC")
t.test(OJdose2$len, VCdose2$len, alternative = "greater")
```
P value is higher than 0.05.  
The null hypothesis is rejected: at dosage of 2mg, there is no significant difference between the two supplement  

###Conclusion for Hypothesis Testing 2
**For dosages of 0.5mg and 1mg, there are significant differences: OJ is better than VC in promoting tooth growth.  At 2mg however, there is no significant differences.**
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
