  
---
title: Exponential Distribution & Central Limit Theorem Comparison
author: "Gerardo Figueroa"
date: "October 19, 2020"
output: pdf_document
---

## Overview
This report pretends to explore the relation between exponential distribution and the Central Limit Theorem (CLT). Lambda will be set to 0.2 for all of the situations. The distribution of the averages of 40 exponentials will be compared over 1000 simulations. 


## Simulations
Seed and set lambda and the exponentials.
```{r}
ECHO=TRUE
set.seed(1337)
lambda = 0.2
exponentials = 40
```

Run the simulations accordingly.
```{r}
simMeans = NULL
for (i in 1 : 1000) simMeans = c(simMeans, mean(rexp(exponentials, lambda)))
```


## Sample Mean &  Theoretical Mean
#### Sample Mean
Calculating the mean from the simulations with give the sample mean.
```{r}
mean(simMeans)
```

#### Theoretical Mean
The theoretical mean of an exponential distribution is lambda^-1.
```{r}
lambda^-1
```

#### Comparison
There is a mild difference between the simulation sample mean and the 
exponential distribution theoretical mean.
```{r}
abs(mean(simMeans)-lambda^-1)
```


## Sample Variance & Theoretical Variance
#### Sample Variance
Calculating the variance from the simulation will result in the sample
variance.
```{r}
var(simMeans)
```

#### Theoretical Variance
The theoretical variance of an exponential distribution is 
(lambda * sqrt(n))^-2.
```{r}
(lambda * sqrt(exponentials))^-2
```

#### Comparison
There is a mild difference between the simulations sample variance and 
the exponential distribution theoretical variance.
```{r}
abs(var(simMeans)-(lambda * sqrt(exponentials))^-2)
```


## Distribution
This is a density histogram of the 1000 simulations. There is an overlay with a 
normal distribution that has a mean of lambda^-1 and standard deviation of 
(lambda*sqrt(n))^-1, the theoretical normal distribution for the simulations.
```{r}
library(ggplot2)
ggplot(data.frame(y=simMeans), aes(x=y)) + 
  geom_histogram(aes(y=..density..), binwidth=0.2, fill="#0072B2", 
                 color="black") +
  stat_function(fun=dnorm, args=list(mean=lambda^-1, 
                                    sd=(lambda*sqrt(exponentials))^-1), 
                size=2) +
  labs(title="Plot of the Simulations", x="Simulation Mean")
```